---
title: "A-19074-2019.09.23"
author: "19074"
date: "2019/9/23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question

Use knitr to produce at least 3 examples(texts,figures,tables).

# Answer 1: Text

### 1.1 Introduction

Here we will introduce a clustering algorithm which is called $K-Means$. Suppose that there is a dataset which may comes from different populations, we'll find a way to divide them into k clusters, the greater the similarity within the group, the greater the difference between groups, the better the clustering effect.

### 1.2 Algorithm

Suppose that the dataset is $\left\{x^{(1)}, \ldots, x^{(m)}\right\}$, for each $x^{(i)} \in \mathbb{R}^{n}$, and we want to assign them to K clusters.

The specific algorithm is as follows:

1. Select K cluster centriods randomly, $\mu_{1}, \mu_{2}, \ldots, \mu_{k} \in \mathbb{R}^{n}$;

2. Repeat the following process until converged:

* For each sample i, calculate the cluster to which it should belong, $c^{(i)} :=\arg \min _{j}\left\|x^{(i)}-\mu_{j}\right\|^{2}$;

* For each cluster j, recalculate the centriod of that cluster, $\mu_{j} :=\frac{\sum_{i=1}^{m} 1\left\{c^{(i)}=j\right\} x^{(i)}}{\sum_{i=1}^{m} 1\left\{c^{(i)}=j\right\}}$.

# Answer 2: Figure

### 2.1 Generate a Dataset and visualize

In this section, we will create a dataset and visualize the data.

```{r}
# Create two groups of points from two different populations
datatest <- rbind(matrix(rnorm(100, sd = 0.3), ncol = 2),
           matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2))
colnames(datatest) <- c("x", "y")

# Visualize the data
plot(datatest)
```

### 2.2 Cluster and visualize

Next, we divide the dataset into two clusters with kmeans function. After clustering, visualize the clusters winch helps present the clustering effects more intuitively.  

```{r}
# Use K-means clustering to divide the whole group into two clusters
kmeanscluster <- kmeans(datatest, 2)

# Visualize the clusters
plot(datatest, col = kmeanscluster$cluster)
points(kmeanscluster$centers, col = 1 : 2, pch = 8, cex = 2)
```

# Answer 3: Table

Finally, we'll have a look at a dataset called state.x77 which is related to the 50 states of the United States of America. We may be interested in the relevance of these data, and we get their correlation coefficient matrix with the cor function and present the results in a table.

```{r}
y <- cor(state.x77)
library(knitr)
kable(head(y), format = "html")
```







