---
title: "Introduction to SC19074"
author: "19074"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19074}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SC19074__ is R package developed to solve the tuning parameter $\lambda$ selection problem in reduced rank regression model. Seven functions are considered, namely, _get_coef_subspace_sim_ (obtain the variance under each lambda by the cofficient matrices) and _rrr.sim6_ (generate random samples) and _stability_ann_sim_(RRR via stability approach) and so on. 

## The main results

```{r}
library(tidyverse)
library(rrpack)
library(knitr)
library(mvtnorm)
library(gridExtra)
library(MASS)
library(xtable)
set.seed(6419)
```

In the reduced rank regression model  via adaptive nuclear norm penalization proposed by Kun Chen, there is no tuning parameter selection method. We apply the stability method. In this problem, we define the instability as: given a lambda, a regression coefficient matrix $\hat C$ can be obtained by applying the reduced rank regression model to each subsample. We define the variance of these matrices as instability. The variance is defined as follows:
$$var(\hat C_{1},\hat C_{2},...\hat C_{n})=(C_{2}^{n})^{-1}\sum_{i<j}d(\hat C_{i},\hat C_{j}).$$
The distance between the two matrices is defined as $$d(\mathcal{A},\mathcal{B})=max{\sigma_{1}(A_{\bot}^{H}B),\sigma_{1}(B_{\bot}^{H}A)},$$ Where $A_{\bot}^{H}$ is the basis of the orthogonal complement of $\mathcal{A}$, and $A$ is a set of orthogonal basis of $\mathcal{A}$.


```{r}
n = 38 # samples
q = 44 # number of response variables
rho = 0.5 # correlation between Xs
rX = 8 # rank of X
r = 5 # rank of C
p = 23 # number of explanatory variables
```


b set to 0.05
```{r}
library(SC19074)
sim21 <- rrr.sim6(n, p, q, r, b = 0.05, rho, rX)
sim_ann21 <- rrr2(sim21$Y, sim21$X, penaltySVD = "ann",
                 modstr = list(gamma = 2))
sim_res21 <- stability_ann_sim(sim21$Y, sim21$X, sim_ann21$lambda, subset = 0.7, ntimes = 100)
```


b set to0.1

```{r}
sim22 <- rrr.sim6(n, p, q, r, b = 0.1, rho, rX)
sim_ann22 <- rrr2(sim22$Y, sim22$X, penaltySVD = "ann",
                 modstr = list(gamma = 2))
sim_res22 <- stability_ann_sim(sim22$Y, sim22$X, sim_ann22$lambda, subset = 0.7, ntimes = 100)
```


b set to 0.3

```{r}
sim23 <- rrr.sim6(n, p, q, r, b = 0.3, rho, rX)
sim_ann23 <- rrr2(sim23$Y, sim23$X, penaltySVD = "ann",
                 modstr = list(gamma = 2))
sim_res23 <- stability_ann_sim(sim23$Y, sim23$X, sim_ann23$lambda, subset = 0.7, ntimes = 100)
```


b set to 0

```{r}
# Rank 0
# Generate X
p = 46
sim4 <- rrr.sim6(n, p, q, r, b = 0, rho, rX)
sim_ann4 <- rrr2(sim4$Y, sim4$X, penaltySVD = "ann",
                 modstr = list(gamma = 2))
sim_res4 <- stability_ann_sim(sim4$Y, sim4$X, sim_ann4$lambda, subset = 0.7, ntimes = 100)
```


```{r}
detach("package:rrpack", unload = TRUE)
detach("package:MASS", unload=TRUE)

# ---- stability-s2n-table ----
# Table of signal to noise ratios for each simulation
s2n_table <- data.frame(Simulation = 1:4, n = n, p = p, q = q, b = c(0, 0.05, 0.1, 0.3),
                       "Signal to noise ratio" = c(sim4$s2n, sim21$s2n, sim22$s2n, sim23$s2n),
                       check.names = FALSE)
print(xtable(s2n_table, label = "tab:stability-s2n-table",
       caption = "Parameters and signal to noise ratios for the four simulated datasets.",
       digits = c(0,0,0,0,0, 2, 3)),
      include.rownames = FALSE)
```


```{r}
# ---- stability-sims-plots ----
stability_combine_sim <- function(stability_ann_results){
  st_plot <- data.frame(rank = c(stability_ann_results$st_res),
                        lambda = rep(stability_ann_results$lambda, each = nrow(stability_ann_results$st_res)))
  st_group <- group_by(st_plot, by = lambda)
  st_sum <- summarize(st_group, var = var(rank), avg = mean(rank)) %>% rename(lambda = by)
  st_sum <- full_join(st_sum, stability_ann_results$st_coef, by = "lambda")
}
stability_plots_sim <- function(sim_results, rank, title = "sim_results", subtitle = ""){
  st_combined <- stability_combine_sim(sim_results)
  # Plot mean vs variance
  varmeanplot <- ggplot(st_combined, aes(x = avg, y = sqrt(var))) + 
    geom_point() +
    geom_vline(aes(xintercept = rank)) +
    xlab("Mean estimated rank") + 
    ylab("Standard deviation of subspace distance") +
    ggtitle(title, subtitle = subtitle) +
    theme_bw()
  # Plot mean vs variance of coefficients
  coefplot <- ggplot(st_combined, aes(x = avg, y = sqrt(var.subspace.coef))) + 
    geom_point() +
    geom_vline(aes(xintercept = rank)) +
    xlab("Mean estimated rank") + 
    ylab(expression(sqrt("Mean of coefficient ranks"))) +
    ggtitle(title, subtitle = subtitle) +
    theme_bw()
  
  return(list(rplot = varmeanplot, coefplot = coefplot))
}
```


```{r}
p21 <- stability_plots_sim(sim_res21, rank = r, title = "Simulation 2", subtitle = "b = 0.05")

p22 <- stability_plots_sim(sim_res22, rank = r, title = "Simulation 3", subtitle = "b = 0.1")

p23 <- stability_plots_sim(sim_res23, rank = r, title = "Simulation 4", subtitle = "b = 0.3")

p4 <- stability_plots_sim(sim_res4, rank = 0, title = "Simulation 1", subtitle = "b = 0")
```

```{r}
# ---- stability-sims-rplots ----
grid.arrange(p4$rplot, p21$rplot, p22$rplot, p23$rplot, nrow = 2)

# ---- stability-sims-coefplots ----
grid.arrange(p4$coefplot, p21$coefplot, p22$coefplot, p23$coefplot, nrow = 2)

# ---- stability-sims-r0-plots ----
grid.arrange(p4$rplot, p4$coefplot, nrow = 1)
```


```{r}
# ---- rank1-sims ----
# Simulations and plots for rank 1 matrices
set.seed(9988999)
n = 38 # samples
q = 44 # number of response variables
rho = 0.5 # correlation between Xs
rX = 8 # rank of X
p = 23 # number of explanatory variables
simr1 <- rrr.sim6(n, p, q, r=1, b = 0.3, rho, rX)
simr1$s2n
sim_annr1 <- rrr2(simr1$Y, simr1$X, penaltySVD = "ann",
                  modstr = list(gamma = 2))
sim_resr1 <- stability_ann_sim(simr1$Y, simr1$X, sim_annr1$lambda, subset = 0.7, ntimes = 100)

simr12 <- rrr.sim6(n, p, q, r=1, b = 0.05, rho, rX)
simr12$s2n
sim_annr12 <- rrr2(simr12$Y, simr12$X, penaltySVD = "ann",
                  modstr = list(gamma = 2))
sim_resr12 <- stability_ann_sim(simr12$Y, simr12$X, sim_annr12$lambda, subset = 0.7, ntimes = 100)

simr13 <- rrr.sim6(n, p, q, r=1, b = 0.1, rho, rX)
simr13$s2n
sim_annr13 <- rrr2(simr13$Y, simr13$X, penaltySVD = "ann",
                  modstr = list(gamma = 2))
sim_resr13 <- stability_ann_sim(simr13$Y, simr13$X, sim_annr13$lambda, subset = 0.7, ntimes = 100)

simr14 <- rrr.sim6(n, p, q, r=1, b = 0, rho, rX)
simr14$s2n
sim_annr14 <- rrr2(simr14$Y, simr14$X, penaltySVD = "ann",
                   modstr = list(gamma = 2))
sim_resr14 <- stability_ann_sim(simr14$Y, simr14$X, sim_annr14$lambda, subset = 0.7, ntimes = 100)

pr1 <- stability_plots_sim(sim_resr1, rank = 1, title = "", subtitle = paste("Signal-to-noise ratio: ", round(simr1$s2n, 2)))
pr12 <- stability_plots_sim(sim_resr12, rank = 1, title = "", subtitle = paste("Signal-to-noise ratio: ", round(simr12$s2n, 2)))
pr13 <- stability_plots_sim(sim_resr13, rank = 1, title = "", subtitle = paste("Signal-to-noise ratio: ", round(simr13$s2n, 2)))
pr14 <- stability_plots_sim(sim_resr14, rank = 1, title = "", subtitle = paste("Signal-to-noise ratio: ", round(simr14$s2n, 2)))
```

```{r}
grid.arrange(pr1$coefplot, pr12$coefplot, pr13$coefplot, pr14$coefplot, nrow = 2)
```






